Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-03 report/report.tex
Rename section: Implementation overview -> Methodology
Add notes about figure origins

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_residential_footpath_compare}
    \caption{Example segments of the Stockholm metropolitan area with highlighted residential streets (left) and footpaths (right). Here can be seen the unique character of footpaths. Walkways in parks appear to grow much more organically, and pavements form rough grid systems with organic branches that bridge over city blocks.}
    \label{fig:residential-footpath-map}
\end{figure}

@@

\section{Implementation overview}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_building_match}
    \caption{Examples of a 1:1 building match (left), where the sought-after building was found both in the OSM (red) and SLU (blue) datasets, and of a 1:n building match (right), where the sought-after building was represented as one polygon in the OSM (red) dataset, but divided into many smaller lots in the SLU (multicolored) dataset.}
    \label{fig:building-match-types}
\end{figure}

@@

The building footprint correspondence will be evaluated using a similarity function that depends on the difference between the turning funcitons of matching building footprints in both datasets.
The turning function was first defined by \textbf{(Arkin et al, 1991)}, as a method for measuring the similarity of two polygons.
The Turning function $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l.
This project uses the turning function as it is defined by \textbf{(Fan et al, 2014)}.
See figure \ref{fig:turning-function} for a side-by-side comparison of a polygon and its turning function.
For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as:
\begin{center}
    $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
\end{center}
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions:
\begin{center}
    $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
\end{center}
The value range will be $(0 < S_{T} < 1)$, where $S_{T}(A,B) = 1$ if the polygons are identical. 
See figure \ref{fig:turning-function-compare} for a side-by-side comparison of two similar polygons and their turning functions.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turn_function}
    \caption{An example of the turning function of a polygon. The edges, vertices and angle of the initial step of the turning funciton are marked.}
    \label{fig:turning-function}
\end{figure}

@@

% Torsdag:
% TODO: Mention that positional accuracy will be the focus early on
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Split up introduction, more subsections
% TODO: Go over all images, add a line about their origins
% TODO: Rename: Implementation overview -> Methodology

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_residential_footpath_compare}
    \caption{Example segments of the Stockholm metropolitan area in OpenStreetMap, with highlighted residential streets (left) and footpaths (right). Here can be seen the unique character of footpaths. Walkways in parks appear to grow much more organically, and pavements form rough grid systems with organic branches that bridge over city blocks. The image was generated using GitHub's geojson viewer.}
    \label{fig:residential-footpath-map}
\end{figure}

@@

\section{Methodology}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_building_match}
    \caption{Examples of a 1:1 building match (left), where the sought-after building was found both in the OSM (red) and SLU (blue) datasets, and of a 1:n building match (right), where the sought-after building was represented as one polygon in the OSM (red) dataset, but divided into many smaller lots in the SLU (multicolored) dataset. The buildings are examples from the OSM and SLU datasets that were prcessed in this projects, and were taken from the Stockholm area.}
    \label{fig:building-match-types}
\end{figure}

@@

The building footprint correspondence will be evaluated using a similarity function that depends on the difference between the turning functions of matching building footprints in both datasets.
The turning function was first defined by \textbf{(Arkin et al, 1991)}, as a method for measuring the similarity of two polygons.
The Turning function $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l.
This project uses the turning function as it is defined by \textbf{(Fan et al, 2014)}.
See figure \ref{fig:turning-function} for a side-by-side comparison of a polygon and its turning function.
For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as:
\begin{center}
    $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
\end{center}
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions:
\begin{center}
    $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
\end{center}
The value range will be $(0 < S_{T} < 1)$, where $S_{T}(A,B) = 1$ if the polygons are identical. 
See figure \ref{fig:turning-function-compare} for a side-by-side comparison of two similar polygons and their turning functions.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turn_function}
    \caption{An example of the turning function of a polygon. The edges, vertices and angle of the initial step of the turning function are marked. The building in the figure was taken from the OSM dataset in the Stockholm area.}
    \label{fig:turning-function}
\end{figure}

@@

% Torsdag:
% TODO: Mention that positional accuracy will be the focus early on
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Split up introduction, more subsections
% TODO: Go over all images, add a line about their origins
